Efficiently summarising relationships in large samples: a general duality between statistics of genealogies and genomes

### 2019-09-06 treestats_paper.tex
flag interpretation that needs clarification

The comparisons are shown in Figure~\ref{fig:chr20}.
Of these methods, branch diversity from tsinfer shows the worst agreement with site diversity,
which is unsurprising as tsinfer makes no attempt to provide well-calibrated node times,
and only aims to provide consistent tree topologies.
The two methods that infer node times differ substantially,
with Relate showing a significantly tighter agreement than GEVA.
Does this mean that Relate is doing a better job at inferring the tree sequence than GEVA?
This is highly suggestive, but not entirely clear.

>>>>

The comparisons are shown in Figure~\ref{fig:chr20}.
Of these methods, branch diversity from tsinfer shows the worst agreement with site diversity,
which is unsurprising as tsinfer makes no attempt to provide well-calibrated node times,
and only aims to provide consistent tree topologies.
The two methods that infer node times differ substantially,
with Relate showing a significantly tighter agreement than GEVA.
\krt{Does this make sense?  If geva is playing with node times based on ts inferred via tsinfer,
    then a difference b/w it and relate is due to the difference in estimating the times, and not the
details of the underlying ts, maybe?}
Does this mean that Relate is doing a better job at inferring the tree sequence than GEVA?
This is highly suggestive, but not entirely clear.
